---
title: "Week 4: Homework"
output: github_document
---

```{r global_options, echo=FALSE, results='asis'}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',  warning=FALSE, message=FALSE)
rm(list=ls())
```
# Question 1

On a 100x100 raster grid, please generate a set of (10 per set)
unconditional simulation maps for each of the following sets of variogram
parameters:

1. sill= 0.5, range = 5, nugget = 0.0001, model = Exponential 
2. sill= 0.5, range = 5, nugget = 0.0001, model = Gaussian 
3. sill= 0.5, range = 50, nugget = 0.0001, model = Exponential 

Based on what you generated, please describe the major visual differences
of the simulated results and explain why. 

```{r q1, echo=T, eval=T}
library(gstat)
# create a empty grid
xy <- expand.grid(1:100, 1:100)
names(xy) <- c('x','y')

# now comment out the following line of codes and make the changes according to the questions. 

# testVgm=vgm(psill=0.025, range=10, model='Gau', nugget=0.0001)

g.dummy <- gstat(formula=z~1, locations=~x+y, dummy=T, beta=1, model=testVgm, nmax=21) 
yy <- predict(g.dummy, newdata=xy, nsim=4)
coordinates(yy)=~x+y
gridded(yy) =TRUE
spplot(yy)

# Now, please comment on the differences of the different variogram models:

```

# Question 2

The `oa.shp` in the `Data` folder is a set of wells containing information
about water level (`WTE`) in feet. Using the `WTE' data for the year of
2013 (field `WTE2013`), please finish the following questions:

1. please interpolate the wells into a continuous surface of water table
   level using simple kriging method and display the estiamted surface.
   Note that `0` in `WTE2013` means no values for those wells.  

2. please also output the map of variance associated with the estimated
   surface and explain what the variance maps tell us. 

3. please run a leave-one-out cross-validation, and calcualte the RMSE
   (root-mean-square deviation) of the estimation. 


